### 2020-01-11 README.Rmd
Add published examples of robvis

>>>>

## Examples of `robvis` in published papers

* Habadi, Mohammed Ibrahim, et al. "[Prevalence of Panic Disorders in the Primary Health Care Setting: A Systematic Review and Meta-Analysis.](https://www.ecronicon.com/ecmi/pdf/prevalence-of-panic-disorders-in-the-primary-health-care-setting-a-systematic-review-and-meta-analysis.pdf)" EC Microbiology 16.1 (2019): 01-09.
* Gibb, Kate, et al. "[The consistent burden in published estimates of delirium occurrence in medical inpatients over four decades: a systematic review and meta-analysis study.](https://www.medrxiv.org/content/medrxiv/early/2019/08/29/19005165.full.pdf)" medRxiv (2019): 19005165.
